国里愛彦 (YOSHIHIKO KUNISATO, Ph.D.)

### 2024-12-01 articles.Rmd
update

- [47] Omizu, T. and Kunisato. Y.(2024). Exploring Effective Intervention Strategies for Depression as a Complex System: Targeted Interventions through Network Simulations. Japanese Psychological Research.

>>>>

- [49] Matsumoto, K., Hamatani, S., Kunisato, Y., Mizuno, Y. (2024). Components of Cognitive Behavioural Therapy for Mitigating Core Symptoms in Attention-Deficit Hyperactivity Disorder: A Systematic Review and Network Meta-analysis. BMJ Mental Health.

- [48] Ishizu, K.,Ohtsuki, T., Shimoda, Y., Kunisato, Y.(2024). ACT in school settings: A pilot study of ACT-based universal group psycho-educational program among Japanese early adolescents. Journal of Contextual Behavioral Science. DOI: https://doi.org/10.1016/j.jcbs.2024.100851

- [47] Omizu, T. and Kunisato. Y.(2024). Exploring Effective Intervention Strategies for Depression as a Complex System: Targeted Interventions through Network Simulations. Japanese Psychological Research. DOI: https://doi.org/10.1111/jpr.12553 [Code](https://osf.io/ta782/)

### 2024-12-01 yoshihiko-kunisato.Rmd
update

### 職歴・教育歴
2008(平成20)年7月～2009(平成21)年3月　医療法人社団更正会　草津病院　非常勤心理士  
2009(平成21)年4月～2011(平成23)年3月　日本学術振興会　特別研究員(DC1)  
2011(平成23)年4月〜2013(平成25)年3月　早稲田大学人間科学学術院　助手(鈴木伸一研究室)  
2013(平成25)年4月〜2015(平成27)年3月　専修大学人間科学部心理学科　講師  
2011(平成23)年5月〜2016(平成28)年3月　独立行政法人　国立精神・神経医療研究センター　技術研究生  
2013(平成25)年5月〜　早稲田大学重点領域研究機構応用脳科学研究所　招聘研究員  
2015(平成27)年4月〜　2021(令和3)年3月専修大学人間科学部心理学科　准教授  
2019(平成32)年4月〜2020(令和２)年3月 Psychological Methods, Department of Psychology,University of Amsterdam 訪問研究員  
2021(令和3)年4月〜　専修大学人間科学部心理学科　教授  
2021(令和3)年〜　国立研究開発法人 国立精神・神経医療研究センター　認知行動療法センター　客員研究員

### 非常勤講師とTA
#### 現在担当中の講義（年度）
2014(平成26)年・2016(平成28)年・2018（平成30）年・2020(令和２)年・2021(令和３)年・2022（令和４）年・2023（令和5)・2024（令和6)　東京大学教養学部統合自然科学科　非常勤講師（講義：認知行動障害論）

>>>>

### 職歴・教育歴
2008(平成20)年7月～2009(平成21)年3月　医療法人社団更正会　草津病院　非常勤心理士  
2009(平成21)年4月～2011(平成23)年3月　日本学術振興会　特別研究員(DC1)  
2011(平成23)年4月〜2013(平成25)年3月　早稲田大学人間科学学術院　助手(鈴木伸一研究室)  
2013(平成25)年4月〜2015(平成27)年3月　専修大学人間科学部心理学科　講師  
2011(平成23)年5月〜2016(平成28)年3月　独立行政法人　国立精神・神経医療研究センター　技術研究生  
2013(平成25)年5月〜　早稲田大学重点領域研究機構応用脳科学研究所　招聘研究員  
2015(平成27)年4月〜2021(令和3)年3月専修大学人間科学部心理学科　准教授  
2019(平成32)年4月〜2020(令和２)年3月 Psychological Methods, Department of Psychology,University of Amsterdam 訪問研究員  
2021(令和3)年〜2025(令和7)年3月　国立研究開発法人 国立精神・神経医療研究センター　認知行動療法センター　客員研究員  
2021(令和3)年4月〜　専修大学人間科学部心理学科　教授

### 非常勤講師とTA
#### 現在担当中の講義（年度）
2014(平成26)年・2016(平成28)年・2018（平成30）年・2020(令和２)年〜2024（令和6)年　東京大学教養学部統合自然科学科　非常勤講師（講義：認知行動障害論）
